Luminance constancy under fixed geometry

### 2018-03-05 Draft2/draft2.tex
DB and JB editing today

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

There is a considerable literature on computational color constancy. Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g. \citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
An important insight of this line of research was that, to account for variation in illumination, it was necessary to consider the light reflected from the entire scene. That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
At the same time, this processing introduces an additional dependence.  Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).  None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$. Additionally, it depends on geometric factors, such as the object's shape and pose, as well as the position of the observer. The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations. Such invariant color perception is called color constancy. (b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy. Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left). Within each row, the surface reflectance of the spheres has the same luminance when illuminated by a standard reference illuminant, CIE D65. The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns. Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.  Within each column, this relative surface reflectance is held fixed. For illustration, we have kept the light source and the background objects fixed across the panels. See Fig.~\ref{fig:studiedCases} for images with such variations. In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
 \end{figure}

>>>>

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly. Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
The computational challenge underlying object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
To produce a stable perceptual representation correlated with an object's surface reflectance the brain must account for these intrinsic factors on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.

Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
A key insight from this work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.  But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant. Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects.

*** HERE ***

At the same time, this processing introduces an additional dependence.  Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image

Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.

***
Subsequent work, which extended the analysis to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS), confirmed this basic insight.

Seminal computational color constancy algorithms applied to a  considered a simplified case in which flat matte surfaces are illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g. \citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., .
Subsequent computational constancy work sought to generalize both the image formation model   None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination spectrum of the light source. It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer. The human visual system is able to account for variations in the reflected light due to such extrinsic factors and produce a percept of object color that is relatively stable with respect to such variations. Such invariant color perception is called color constancy. (b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy. Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left). Within each row, the surface reflectance of the spheres has the same luminance when illuminated by a standard reference illuminant, CIE D65. The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns. Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.  Within each column, this relative surface reflectance is held fixed. For illustration, we have kept the light source and the background objects fixed across the panels. See Fig.~\ref{fig:studiedCases} for images with such variations. In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
 \end{figure}
 % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.
